# Annotations: infinite positions

## What is the problem?
To position annotations at the edge of a plot, the values `Inf` and `-Inf` can
be passed to the positioning aesthetics (e.g., `x`) of `ggplot2::annotation()`.
This technique fails for scales that are of class `Date`.

## What is an example?
It is useful to first see how we can position annotations on scales which aren't
dates. For example, using the built-in economics dataset of ggplot2, we can postion an annotation in the top-right corner of the plot like so:

```{r}
library(ggplot2)

ggplot(economics, aes(x = pop, y = unemploy)) +
  geom_point() +
  annotate(
    "text",
    label = "Top-right",
    vjust = 1, hjust = 1, # Prevent text being chopped
    x = Inf, y = Inf
  )
```

When we try the same approach to a scale that uses dates, we get an error:

```{r}
#| error: true
ggplot(economics, aes(x = date, y = unemploy)) +
  geom_point() +
  annotate(
    "text",
    label = "Top-right",
    vjust = 1, hjust = 1, # Prevent text being chopped
    x = Inf, y = Inf
  )
```

## What is a soltuion?
To plot an annotation at the edge of a scale of class `Date`, you should change
the class of `Inf` to a `Date` class:

```{r}
ggplot(economics, aes(x = date, y = unemploy)) +
  geom_point() +
  annotate(
    "text",
    label = "Top-right",
    vjust = 1, hjust = 1, # Prevent text being chopped
    x = structure(Inf, class = "Date"), y = Inf
  )
```

See [this](https://github.com/tidyverse/ggplot2/issues/4308) GitHub issue for
more information.