# Annotations: text size

## What is the problem?
When adding a text annotation to a plot with `ggplot2::annotate()`,
the size of the text in the annotation does not match other elements on the
plot despite setting the `size` argument to equal values.

## What is an example?

```{r}
library(ggplot2)

ggplot() +
  ggtitle("This title is size 14") +
  theme(plot.title = element_text(size = unit(14, "pt"))) +
  annotate(
    "text",
    label = "This annotation is size 14",
    x = 0, y = 0,
    size = unit(14, "pt")
  )
```

## What is a solution?
To align the sizes of annotations and other elements on the plot, annotation
sizes must be divided by `.pt`:

```{r}
ggplot() +
  ggtitle("This title is size 14") +
  theme(plot.title = element_text(size = unit(14, "pt"))) +
  annotate(
    "text",
    label = "This annotation is size 14",
    x = 0, y = 0,
    size = unit(14, "pt") / .pt # divide by .pt
  )
```

This works because `annotate()` calculates font size by multiplying the specified
size by the global variable `.pt` (equal to  `2.845276`). See [this](https://stackoverflow.com/questions/65076492/ggplot-size-of-annotate-vs-size-of-element-text) Stack Overflow post for more
information.
