# Panel sizes

## What is the problem?
There is no default method to set the panel size of a plot in ggplot2, only a
method to set the plot size using the `width` and `height` paramaeters of
`ggplot2::ggsave()`. The panel refers to the inner plotting window that contains
the data, and the plot refers to the whole plotting window that contains both
the panel and all other elements (e.g., legeneds, labels, etc.):

```{r}
#| echo: false
library(ggplot2)

ggplot() +
  ggtitle("Plot") +
  theme(plot.title = element_text(size = unit(14, "pt"), hjust = 0.5)) +
  annotate(
    "text",
    label = "Panel",
    x = 0, y = 0,
    size = unit(14, "pt") / .pt
  )
```

## What is a solution?
The [`ggh4x::force_panelsizes()`](https://teunbrand.github.io/ggh4x/reference/force_panelsizes.html)
function can be used to coerce a single panel to a set size:

```{r}
library(ggplot2)

ggplot(economics, aes(x = pop, y = unemploy)) +
  geom_point() +
  ggh4x::force_panelsizes(
    rows = unit(8, "cm"),
    cols = unit(12, "cm")
  )
```