# Consecutive true values

## What is the problem?
For a column of logical values in a data frame, count of the  number of
consecutive `TRUE` values at the given point in the column. `NA` values should
return `NA` and reset the count.

## What is an example?
For the data frame:

```{r}
df <- tibble::tibble(x = c(TRUE, TRUE, NA, TRUE, FALSE, TRUE, TRUE, TRUE))
```

The following data frame should be returned:

```{r}
#| echo: false
tibble::tibble(
  x = c(TRUE, TRUE, NA, TRUE, FALSE, TRUE, TRUE, TRUE),
  consecutive_trues = c(2, 1, NA, 1, 0, 3, 2, 1)
)
```

## What is a solution?
We can leverage the `dplyr::consecutive_id()` function to create unique group
id's, and then create sequences along these id's:

```{r}
#| warning: false
library(tibble)
library(dplyr)

df |>
  mutate(consecutive_trues = consecutive_id(x)) |>
  mutate(consecutive_trues = seq(n(), 1), .by = consecutive_trues) |>
  mutate(consecutive_trues = if_else(x, consecutive_trues, 0))
```

To reverse the order of the count of `TRUE` values, that is, to count the
number of trailing `TRUE` values, the order of the sequence can simply be
switched.
